A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
tightening up the discussion a little bit

# DISCUSSION
Our continuous urbanization index showed a significant phylogenetic signal [@revell2008phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence, @ibanez2017global, @sol2017urbanisation, @la2018phylogenetic]. This contrasts with previous studies [@evans2011makes], but is likely a result of sample size considerations. Niche breadth, as measured by generalism, was significantly associated with our urbanization index across both phylogenetic and non-phylogenetic analyses, confirming the notion that urban birds have broad environmental tolerance [@bonier2007urban]. Conversely, granivores and insectivores were consistently selected against. Residual brain mass was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade, the species with the largest residual brain mass are most readily observed in urban areas. A similar pattern was found for body size, although not significant.

**A PARAGRAPH ON SPECIFIC TRAITS AND CITATIONS WHICH CONFIRM OR DENY THEM**

 Fully understanding specific species' traits which are associated with urban birds allows us to fully understand how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes]. However, previous studies which have assessed this have generally focused on discrete classifications of species based on their responses to urbanization, limiting the applicability of results found. We further highlight that our analysis used a total of 477 species (Appendix 4), greater than many previous studies, ultimately allowing for more generalizable results. The aforementioned differences in our study compared with others is likely a result of our increased sample size, as well as our use of a continuous measure of urbanization.

Our results suggest that urbanization selects against specialist species, granivores, and insectivores. As such, future urban development should focus on maintaining a high diversity of habitat (CITATIONS) both for foraging (CITATION) and nesting (CITATIONS). Further, a focus should be on providing habitat for insects (CITATION), which will in turn increase the presence of insectivores in urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global, @aronson2016hierarchical, @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with advancing remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role, @lepczyk2017global], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (i.e., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full, @marra2015call]. Further, future studies should look to expand this analysis outside of the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales (i.e., does city size affect the patterns found here; [@sol2017urbanisation, @batary2017non]).

Ultimately, we provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments. In doing so, we highlight the applicability of broad-scale empirical data to assess species' traits which predict presence and adaptability in urban environments. Our results suggest that generalist species are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. Australia is a relatively young country and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [CITATION]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved modelling performance.

>>>>

# DISCUSSION
Our continuous urbanization index showed a significant phylogenetic signal [@revell2008phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence, @ibanez2017global, @sol2017urbanisation, @la2018phylogenetic]. This contrasts with previous studies [@evans2011makes], but this contrasting finding is likely a result of sample size considerations. Niche breadth, as measured by different types of generalism, was significantly associated with our urbanization index across both phylogenetic and non-phylogenetic analyses, confirming the notion that urban birds have broad environmental tolerance [@bonier2007urban]. Conversely, granivores and insectivores were consistently selected against in urban areas. Residual brain mass, and body size to an extent, was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade, the species with the largest residual brain mass and large body size are most suited to surviving in urban areas.

Our finding that ecological generalists are more readily observed in urban areas confirms that of other work [@mckinney2006urbanization, @bonier2007urban, @moller2009successful]. We also confirm work which has found a relationship between annual fecundity and urbanization in birds [@croci2008does, @moller2009successful]. While some studies have found a lack of evidence that relative brain size is critical in urban birds [@kark2007living, @evans2011makes], we confirm those which do support the hypothesis that brain size is heavily correlated with urban birds [@moller2009successful, @maklakov2011brains, @moller2015brain]. Furthermore, we do confirm that urbanization appears to select against insectivorous species [@chace2006urban, @evans2011makes]. While others have found that urbanization supports granivorous species [@chace2006urban, @kark2007living, @evans2011makes], we found the opposite trend, but this could be a result of relatively little supplementary feeding in Australian cities [@fuller2008garden]. We did not find any strong support for our hypotheses on different nesting types, but we did find that in general, species which tended to be more social were at an advantage to city living, confirming previous studies [@kark2007living].

Clearly, many traits have been used to identify a species' adaptability with urban-living (e.g., Appendix 1), but often times results differ among studies. Fully understanding the suite of specific species' traits which are associated with urban birds allows for a better understanding of how to best preserve and maintain avian biodiversity in urban areas [@evans2011makes]. As previously noted, a major shortcoming of previous studies has been the focus on discrete classifications of species based on their responses to urbanization. Our analysis used a total of 477 species (Appendix 4), more than any similar study, to the best of our knowledge. Furthermore, our models assessed the applicability of traits in relation to one another (i.e., we did not run separate models or statistical tests for each specific trait as previously done). The aforementioned differences in our study's results compared with others is likely due to increased sample size, as well as our use of a continuous measure of urbanization. Our results suggest that urbanization selects against specialist species [@sorace2009distribution], granivores, and insectivores. As such, future urban development aimed at increasing avian diversity should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat]. A species-specific approach to assess particular resources necessary for specialist species may be necessary. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments (CITATION), which will in turn increase the presence of insectivorours bird species in urban environments.

Global broad-scale empirical datasets are rapidly expanding our knowledge of urbanization impacts on birds [e.g., @aronson2014global, @aronson2016hierarchical, @gutierrez2018citizen], in large part due to the growing use of citizen science data [@silvertown2009new] in combination with advancing remote sensing technology [@gorelick2017google]. We used a novel approach, over a broad spatial and temporal scale, to quantify an urbanization index in birds. We did not explicitly account for changes throughout the annual cycle in a species' association with urban areas [e.g., @la2014role, @lepczyk2017global, @katewaleffect], but migratory status was considered as a predictor. We highlight that future studies, especially within migrant-dominated landscapes (i.e., Europe, North America), should account for changes in a species' response to urbanization throughout the full-annual cycle [@hostetler2015full, @marra2015call]. Further, future studies should look to expand this analysis outside of the scope of Australia, and also investigate whether these patterns hold true at multiple spatial scales (i.e., does city size affect the patterns found here; [@sol2017urbanisation, @batary2018non]).

Ultimately, we provide the largest study to date using a continuous urbanization metric in order to assess biological and ecological traits which predict a species' adaptability to urban environments. In doing so, we highlight the applicability of broad-scale empirical data to assess species' traits which predict presence and adaptability in urban environments. Our results suggest that generalist species, with large relative brain size, are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. Australia is a relatively young country with rapid urbanization currently underway [@coffee2016visualising] and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [@hallmann2017more]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved predictive performance.
